Adaptative neigbouring methods applied to telephonic base stations

### 2024-08-14 article.tex

\subsection{Delaunay triangulation}
\noindent The Delaunay triangulation is named after Boris DELAUNAY for his work on it from 1934 [citer l'article].

A Delaunay triangulation of a set of points in the plane subdivides their convex hull into triangles whose circumcircles 
do not contain any of the points. You can find an illustration of this method in Figure~\ref{del_tri}.

>>>>

\subsection{Delaunay triangulation}
\noindent The Delaunay triangulation is named after Boris DELAUNAY for his work on it from 1934 \cite{art_delaunay}.

A Delaunay triangulation of a set of points in the plane subdivides their \gls{convHull} into triangles whose circumcircles 
do not contain any of the points. You can find an illustration of this method in Figure~\ref{del_tri}.
